Network Configuration Synthesis with Abstract Topologies

### 2016-11-14 paper/abstraction/paper.tex
more edits

The annotation $mincut(X)$ appearing on a n edge in an assertion about the fault tolerance between nodes in two roles. The rule \infrule{I-mincut} uses such assertions. To each node in role $n$, we can construct at least the minimum of $X$ and $k$ disjoint paths.

>>>>

The annotation $mincut(X)$ appearing on an edge in an assertion about the fault tolerance between nodes in two different roles. The rule \infrule{I-mincut} uses such assertions. To each node in role $n$, from a node in role $m$, we can construct at least the minimum of $X$ and $k$ disjoint paths.
